An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-10-30 mixedwindow.tex
Add notation and clarification to beginning of appendix
- Defines a few terms that had been accidentally deleted at the beginning
  of the appendix
- Add text specifying that the proofs are for scalars.
Rephrase parts of proof of Theorem 1

Define the additional notation 
$F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
$F_t = F_t(\btrue)$,
and
$h_t = h_t(\btrue)$.

\begin{proof}[Proof of Theorem \ref{res:1}]
  Replace $R$ with $\log(T)$ and $P$ with $T - \log(T)$ in the
  statistic; this substitution does not affect its asymptotic
  distribution.
  As in \citet{Wes:96} and \citet{WeM:98}, expand $\fh_t$ around
  $\btrue$ to get
  \begin{align*}
    \sqrt{P} \big(\fb - \fb(\btrue)\big) &= \oclt{t}
    \big(f_t - \E f_t\big) +
    \E F_t B \oclt{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t
  \end{align*}
  where (again, as in \citealp{Wes:96}) the $i$th element of $w_t$ is
  \begin{equation*}
    w_{it} = \tfrac12 (\bh_t - \btrue)'
    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'}
    f_{it}(\bt_{it}) \Big]
    (\bh_t - \btrue)
  \end{equation*}
  and each $\bt_{it}$ lies between $\bh_t$ and
  $\btrue$; $\oclt{t} w_t = o_{p}(1)$ as in Theorem~\ref{res:3}.
  Then, as before,
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12}\\
  \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  from Lemma~\ref{res:a4}.  The formula of the asymptotic variance can
  be derived exactly as in \citet{Wes:96} and \citet{WeM:98}.

  Note that \[f_t(\btrue)= 2 (y_{t+1} -
  x_t'\btrue)(\yh_{1,t+1} - x_t'\btrue) \quad \text{a.s.},\] as
  in \citet{ClW:07}, which is an \mds, so we do not need to use a
  \hac\ estimator of the variance under the null.  Also observe that
  \[F_t(\beta) = 2 x_t(x_t'\beta - \yh_{1,t+1}) + 2 x_t(x_t'\beta -
  y_{t+1})\] and the second term is an \mds\ under the null,
  explaining the particular form of $g_t(\beta)$.
\end{proof}

\begin{proof}[Proof of Theorem \ref{res:2}]
  Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
  Theorem~\ref{res:3} of this paper and Theorems~3.1 and~4.1 of
  \citet{RoW:05} complete the proof.
\end{proof}

>>>>

Define the additional notation 
$f_t = f_t(\btrue)$,
$F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
$F_t = F_t(\btrue)$,
$h_t = h_t(\btrue)$,
and
\begin{equation*}
  H_{t} = \tfrac1t \sum_{s=1}^t h_{s}.
\end{equation*}
All of the proofs in this section will be presented for the case where
there is a single alternative model. The Cram\'er-Wold device ensures
that the corresponding multivariate results follow trivially.

\begin{proof}[Proof of Theorem \ref{res:1}]
  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
  \begin{equation*}
    \sqrt{P} (\fb - \E \fb(\btrue))
    = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
      + \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^{R'} (\fh_t - \E f_t).
  \end{equation*}
  Lemma~\ref{res:a1} ensures that the second term is $o_p(1)$, and
  we can rewrite this summation as
  \begin{align*}
    \sqrt{P} (\fb - \E \fb(\btrue))
    &= \ocltb{t} (f_t - \E f_t) + \E(F_t) B \ocltb{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
  \end{align*}
  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.

  Lemma~\ref{res:a4} shows that
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12} \\
    \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
  w_t = o_{p}(1)$. Finally,
  \begin{equation*}
    \oclt{t} (f_t - \E f_t,\ H_t)' \to^d N(0, S)
  \end{equation*}
  using the same argument as \citet{Wes:96}.
\end{proof}
